\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm} LFEUI - Investigation Proposal \\ \vspace{4mm} {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-1mm}

### 2023-12-02 text/LogBooks/logbook1.tex
logbook 1

On the 30\textsuperscript{th} of November, the four members of our group went to the second meeting with professors Rodrigo Mateus, Rui \_\_ and Norberto \_\_ at CTN Loures. Our goal was to discuss the work we will be doing in the following session at the same laboratory.
We arrived at 9:30 AM and started discussing the questions that we had been requested to answer the previous session.

@@

\begin{enumerate}
  \item The structure of the tandem 2.5 MeV accelerator and both it's acceleration tubes. They allow the proton beam to reach the target with a kinetic energy of 5 MeV instead of 2.5 MeV (only one tube);
  \item The radiation at the laboratory - we were told that the radiation levels are very low unless we were very close to the accelerator.
  \item The vacuum inside the tubes - we estimated that, at a pressure of $10^{-7}$ mbar (the pressure inside the tubes), there are approximately $10^9$ particles per cubic centimeter. This is a good vacuum meaning that the protons won't collide with other particles and will be able to reach the target without losing energy;
  \item The equation that we aim to study: a proton collides with $^7$Li and produces $^8$Be, which then decays into two alpha particles. The decay process is not detectable, so we will only be able to detect the alpha particles:

@@

  \item The importance of the electromagnets used to deviate the trajectory of the proton beam. We understood that deflection angle is related to the mass and charge of the particle, therefore different particles will have different trajectories, meaning we can isolate the protons on the incident beam;
  \item Samples used: in the next session, we are going to work with need to collect the radiation spectrum of two different Lithium-7 samples: one of them is glass sample composed of silicon, boron and lithium and the other one is a implant sample, which is a thin layer of lithium implanted in a silicon substrate;
  \item Finally, we discussed the expected results for both samples - phenomena such as Rutherford Backscattering, Elastic Scattering and profile of the energy spectrum of the alpha particles were mentioned.
\end{enumerate}

>>>>

On the 30\textsuperscript{th} of November, the four members of our group went to the second meeting with professors Rodrigo Mateus, Rui Silva and Norberto Catarino at CTN Loures. Our goal was to discuss the work we will be doing in the following session at the same laboratory.
We arrived at 9:30 AM and started discussing the questions that we had been requested to answer the previous session.

@@

\begin{enumerate}
  \item The structure of the tandem 2.5 MeV accelerator and both it's acceleration tubes. They allow the proton beam to reach the target with a kinetic energy of 5 MeV instead of 2.5 MeV (only one tube);
  \item The radiation at the laboratory - we were told that the radiation levels are very low unless we were very close to the accelerator.
  \item The vacuum inside the tubes - we estimated that, at a pressure of $10^{-7}$ mbar (the pressure inside the tubes), there are approximately $10^9$ particles per cubic centimeter. This is a good vacuum meaning that the protons won't collide with other particles and will be able to reach the target without losing energy because the mean free path is longer than the accelerator;
  \item The equation that we aim to study: a proton collides with $^7$Li and produces $^8$Be, which then decays into two alpha particles. The decay process is not detectable, so we will only be able to detect the alpha particles:

@@

  \item The importance of the electromagnets used to deviate the trajectory of the proton beam. We understood that deflection angle is related to the mass and charge of the particle, therefore different particles will have different trajectories, meaning we can isolate the protons on the incident beam;
  \item Samples used: in the next session, we need to collect the radiation spectrum of two different Lithium-7 samples: one of them is a glass sample composed of silicon, boron and lithium and the other one is a implant sample, which is a thin layer of lithium implanted in a silicon substrate;
  \item Finally, we discussed the expected results for both samples - phenomena such as Rutherford Backscattering, Elastic Scattering and profile of the energy spectrum of the alpha particles were mentioned.
\end{enumerate}

### 2023-12-02 text/proposta/prop.tex
logbook 1

\title{\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm}
LFEUI - Investigation Proposal\vspace{-5mm}}
\date{November 2023}

@@

@@

@@

@@

>>>>

\title{\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm}
LFEUI - Investigation Proposal \\ \vspace{4mm} {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-1mm}}
\date{November 2023}

@@

\paragraph*{}

Our main goal is to develop a scientific research project alongside three senior investigators from CTN (Centro Tecnológico e Nuclear), Rodrigo Mateus, Rui Silva and Norberto Catarino.

Our project will be focused on the detection of Li in technological materials through nuclear reactions. The main motivation for this project is to study and develop a detection technique for elements such as Li and Br with high sensitivity.

Through the year there have been multiple techniques with the same purpose such as atomic spectroscopy and ?. Particularly, the one we aim to use was introduced in ?.

@@

\paragraph{Set-up}

The experimental set-up consists of a Tandem accelerator, a beam line with an electromagnet and a chamber with the samples and the detectors.
The accelerator produces a beam of protons with a kinetic energy of 5 MeV which is deviated by the electromagnet and hits the samples. 
The electromagnets deflect particles with different angles according to their charge-to-mass ratio.
This allows us to remove any unwanted particles from the beam and only let the protons pass through.
The detectors used are silicon detectors - these detect charged particles through the ionization they produce in the silicon.

In addition, their are connected to a electronic system that amplifies the signal and sends it to a computer where we can see the results.
We aim to analyze the energy spectrum resulting from the reaction between the protons and the samples.
These spectra will unveil the presence of Li in the samples.

\paragraph{Samples}

We are going to work with two different Lithium-7 samples: one of them is a glass sample composed of silicon, boron and lithium and the other one is a implant sample, which is a thin layer of lithium implanted in a silicon substrate.

\paragraph{Requirements}

@@

\paragraph*{}

In order to complete our project we will need one full day of beamtime at the CTN laboratory. Alongside this day, we will also meet with the investigators at CTN for another two mornings to discuss the project, before the experiment and the results after the experiment:

\begin{table}[H]
\centering
\begin{tabular}{|w{0.45\linewidth}|w{0.3\linewidth}|w{0.15\linewidth}|}
\hline
Phase & Date & Duration \\ \hline
Theoretical Background, Planning and Lab Overview & 30/11/2023 9h30 & 4h \\ \hline
Experiment & 7/12/2023 8h00 & 8h \\ \hline
Results Discussion & ?? 9h30 & 4h \\ \hline
\end{tabular}
\end{table}

@@

\paragraph{}
